\TheTitle

### 2016-04-26 linvis.tex
Merge-Tree model edited

\newif\ifdraft
%\drafttrue

@@

@@

Git uses a Directed Acyclic Graph (DAG) as its main data model. In this model, a commit has one or more ordered parents (ancestors), except the root commits of a repository which
do not have ancestors--Linux git repository has two such commits. Commits are divided into merge commits (they merge two or more branches) and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or more. The order of the parents matter: the first parent is the branch in which
the merge is being done; while the rest indicate the branches being merged (git allows any number of branches to be merged at the same time). Their order in the
parents relationship indicate the order in which the branches are being merged (second parent first, third parent second, etc.).

In Git, commits are immutable. Once they are created, they never change. Git allows operations to alter commits or to reorder them. However, in such case, the
commit changes its commit id, effectively becoming a new commit. This means that commits do not record the branches or repositories they have traversed in their
way to master.
For instance, assume the sequence of commits  exemplified in Figure~\ref{fig:repoEvents}. In this case commits are performed in various repos and branches. The
DAG representation of these commits is shown in Figure~\ref{fig:repoDAG}. Notice that this DAG loses information about what repository is Master (in fact, it
loses all information about what repositories any commit has passed through). The merge-tree view of this DAG is shown in Figure~
\ref{fig:repoTree}. Note that the direction of the edges of the DAG has been inverted. Instead of pointing to the ancestors, it points to its successors (the path to
Master). Also, the DAG has been simplified, and it only shows for any commit, one edge (its path to Master).

@@

Computing the tree-model of a DAG of any repository might not be possible. However, certain features of the development process of Linux make it feasible to
compute its merge-tree. In particular, the Master branch of Linux is maintained by Linus Torvalds and only him has write access to it. We have verified this
assertion if previous research~\cite{German2015}. We have developed a heuristic that is presented in Algorithm~\ref{fig:alg}. In a nutshell, first identify the commits directly made
to the master branch. Then,
recursively, for
every commit, using the DAG, determine the shortest path (in terms of time) from such commit to master using the inverted DAG.

@@

We use this information to evaluate the accuracy of the merge tree-model extracted from the DAG. We therefore compare, for commits with no conflict: a) the number of
non-merge commits, b) the summaries of the commits available in the log, and c) the summaries of the merges included.

The results of this verification show that this heuristic detected no incorrect merges since 2013, two incorrect merges in 2012, and two in 2011. However, this
heuristic breaks apart on Oct 15, 2009 due
to the presence of so-called foxtrot commits that confound the true Master branch of a repository \footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and no longer works for older merges.

@@

The modules tab (figure \ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by git, and are not going to
be present in all repositories.  In the Linux repository, authors put the module
they are working on in the one-line preview of the log-message; for example: the log \emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module
(the coverage testing tool of the kernel). We heuristically
extract the module by taking all text in the log preview of commits until the first
colon.  Modules are logical partitions of the information in the kernel. Depending
on where the author was working, modules can be general, such as ``bluetooth'' and
``wireless'', or can be quite specific for individual hardware, such as
``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit does not
correctly follow this format and the hueristic approach fails. As with the Files panels,
non-merge commits show their corresponding information, but for merge commits we aggregate all the modules changed
in all the commits that are part of that merge.
The output of this view is shown in Figure~\ref{fig:modules}.

@@

Version control systems monitor the development lifetime of software projects. This
makes the version control system vital in providing information about how a software
project is being developed. To our knowledge, we know of no git repository
visualization tool that builds a tree that maps the path a commit follows to the
master branch from the DAG provided by git. This may be because more information is
required to generate the tree-model than what is stored by git. However, there has
been a lot of work in providing visualizations of various repositories.

>>>>

\newif\ifdraft
\drafttrue

@@

\evantodo {
        \begin{enumerate}
                \item Add simplified abstract -- From email
                \item replace figure reference with Figure~\\ref
                \item Check captions
                \item gitk to Gitk
                \item git to Git
                \item diff to patch
                \item id to ID
        \end{enumerate}
}

@@

Git uses a directed acyclic graph (DAG) as its main data model. In this model, a
commit has one or more ordered parents (ancestors), except the root commits of a
repository which do not have ancestors--Linux git repository has two such commits.
Commits are divided into merge commits, merging two or more branches, and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or
more. The order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged (git allows
merging multiple branches simultaneously). The second parent is the first branch
merged, the third parent is the second branched merged.

Once a commit is created, it is never changed. Git allows operations to alter
commits or reorder them, but it changes the commit id in the process, effectively
making a new commit. This makes commits unable to record the traversal of merges
from the commit to the merge into the master branch.

A short example: assume the of commits represented in figure \ref{fig:repoEvents}
shows the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
figure \ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in figure \ref{fig:repoTree}. Note that the direction of the
edges of the DAG has been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

Computing the merge-tree from a DAG for any repository may not be possible; however,
certain features of the development process of Linux make it feasible to compute the
merge-tree for the Linux repository. First, the master branch of Linux is maintained
by Linus Torvalds, and only Linus has write access to it. We have verified this
assertion in previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first identifies
the commits made directly to the master branch; whereafter it recursively determines
the shortest path (in terms of time), using the DAG, from each commit to master
using the inverted DAG.

@@

We use this information to evaluate the accuracy of the merge-tree model extracted
from the DAG. For commits with no conflicts, we compare: 1) the number of non-merge
commits, 2) the summaries of the commits available in the log, and 3) the summaries
of the merges included.

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October 15 2009 due to the
presence of \textit{foxtrot} commit, which confounds the true master branch of a
repository \footnote{See
        \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a
        description of the issue}, and will not work for older merges.

@@

The modules tab (figure \ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by git, and are not going to
be present in all repositories.  In the Linux repository, authors put the module
they are working on in the one-line preview of the log-message; for example: the log \emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module
(the coverage testing tool of the kernel). We heuristically
extract the module by taking all text in the log preview of commits until the first
colon.  Modules are logical partitions of the information in the kernel. Depending
on where the author was working, modules can be general, such as ``bluetooth'' and
``wireless'', or can be quite specific for individual hardware, such as
``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit does not
correctly follow this format and the heuristic approach fails. As with the Files panels,
non-merge commits show their corresponding information, but for merge commits we aggregate all the modules changed
in all the commits that are part of that merge.
The output of this view is shown in Figure~\ref{fig:modules}.

@@

Version control systems monitor the development lifetime of software projects. This
makes the version control system vital in providing information about how a software
project is being developed. To our knowledge, we know of no git repository
visualization tool that builds a tree that maps the path a commit follows to the
master branch from the DAG provided by git. This may be because more information is
required to generate the merge-tree model than what is stored by git. However, there
has been a lot of work in providing visualizations of various repositories.
